Evaluating the Supportive Effect of Feature Selection Methods on Machine Learning Models in Monitoring Forest Health Using Hyperspectral Remote Sensing Data

### 2020-04-07 docs/00-manuscripts/ieee/ieee-manuscript.tex
A.B. review: rephrase feature set differences

\subsubsection{Feature set differences}
One objective which this study aimed to answer was whether expert-based or data-driven feature engineering has a positive influence on model performance.
With respect to \autoref{fig:perf-result} one can say that overall the different feature sets did not result in substantial changes in performance.
RF and XGBoost showed a somewhat surprising decrease in performance of about six percentage points on task VI compared to all others.
We have no explanation for this specific result, especially because the SVM does not show this difference.

>>>>

\subsubsection{Feature set differences}
One objective which this study aimed to answer was whether expert-based or data-driven feature engineering has a positive influence on model performance.
With respect to \autoref{fig:perf-result} one can say that overall the different feature sets did not result in substantial and consistent changes in performance.
RF and XGBoost showed a somewhat surprising decrease in performance of about six percentage points on task VI compared to all others.
We have no explanation for this specific result, especially because the best performing SVM model does not reflect this difference.
In addition, all learners showed a slightly better average performance on feature sets which included NRIs (e.g. NRI-VI, HR-NRI, HR-NRI-VI) than on those which did not (i.e. VI and HR only).
